---
title: Web Scraping Amazon.ca
author: ''
date: '2022-03-27'
slug: web-scraping-amazon-ca
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2022-03-27T17:08:15-04:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

Find this project on my Github [here](https://www.google.com "Google's Homepage")

### **Main Objective**
Attribute changes in apparent thermal conductivity in monitoring intervals to hydrological features or errors due to DTS data collection or processing

### **Presented in this report**

Plots of each monitoring interval isolated in SEN-06 multilevel system with 6 A-DTS snapshots accompanied by 

1. Temperature plots of each test at each depth discrete measurement within monitoring interval determined by the A-DTS sampling resolution
  - is the slope poorly fit resulting in unreliable thermal conductivity?
  
2. Instantaneous apparent thermal conductivities at each depth 
  - how consistent is the instantaneous thermal conductivity with time compared to the overall thermal conductivity
  
3. ATV amplitude images
  - attribute changes in thermal conductivity between tests with specific fractures/features
  
### **Work In Progess**

- there is a problem with the instantaneous thermal conductivities for 2018_08_MLS generated with the "fit_convolve" function which I have not solved yet

```{r setup, include=FALSE}
library(ggplot2)
library(data.table)
library(dplyr)
library(dts)
library(tibble)
library(duckdb)
library(tidyverse)
library(plotly)
library(knitr)
library(gridExtra)
library(cowplot)
knitr::opts_chunk$set(echo = TRUE)
```

<!-- This chunk reads in all the data -->

```{r echo=FALSE, warning=FALSE}

# 1. read in port location data
# ports <- data.table(read.csv("data/port_data.csv"))
ports <- fread("data/port_data.csv")

# 2. read in thermal conductivity data
# therm <- (data.table(read.csv("data/thermal_conductivity.csv")))[,X := NULL]
therm <- fread("data/thermal_conductivity.csv")[,V1 := NULL]

# 3. read in temperature data
temp <- fread("data/all_temperature_data.csv")[,c("V1", "variable"):=NULL]

# 4. read in instantaneous thermal conductivites
data <- readRDS("data/instantaneous_03_16.rds")
instant <- data[[1]]
overall <- data[[2]]
overall$depth <- as.double(levels(overall$depth))[overall$depth]
instant$depth <- instant$depth 
overall$depth <- overall$depth 

# 6. read in ATV amplitude
amp <- readRDS("data/amplitude.rds")

# now set distance intervals for atv data
# to do this, extract distance from processed dts data
x <- therm[test=="2018_08_MLS"]
intervals <- x$depth
```

### All Thermal Conductivity Data 

```{r echo=FALSE, warning=FALSE, fig.width=10, fig.height=10} 
intercepts <- append(ports$TopDepth, ports$BottomDepth)

full_therm <- ggplot(therm, aes(depth, Therm_con, group = test, color = test)) + 
          geom_line(size=1.05) +
          ylim(c(0,10)) +
          scale_x_reverse() +
          coord_flip() +
          geom_vline(xintercept=intercepts) +
          ggtitle("Port Thermal Conductivities") +
          ylab("Thermal Conductivity (W/mK)") +
          xlab("Depth Below Ground Surface (m)") +
          theme(legend.position = 'none')

#full_therm <- ggplotly(full_therm)

full_rsq <- ggplot(therm, aes(depth, rsq, group = test, color = test)) + 
          geom_line(size=1.05) +
          ylim(c(0,1)) +
          scale_x_reverse() +
          coord_flip() +
          geom_vline(xintercept=intercepts) +
          ggtitle("R Squared") +
          ylab("Thermal Conductivity (W/mK)") +
          theme(axis.title.y = element_blank(),
                axis.title.x = element_blank())
          # theme(legend.position = 'none')

#full_rsq <- ggplotly(full_stats)

full_stderror <- ggplot(therm, aes(depth, ste, group = test, color = test)) +
          geom_line() +
          ylim(c(0,0.05)) +
          scale_x_reverse() +
          coord_flip() +
          geom_vline(xintercept=intercepts) +
          ggtitle("Standard Error") +
          ylab("Thermal Conductivity (W/mK)") +
          theme(axis.title.y = element_blank(),
                axis.title.x = element_blank()
                )

#full_stderror <- ggplotly(full_stderror)

plot_grid(full_therm, full_rsq, ncol=2, rel_widths = c(2/3, 1/3))
# a <- subplot(full_therm, full_stats, shareX = TRUE, shareY=FALSE)
# a %>% style(t, showlegend=FALSE, traces=6:14)
```